Pricing Games in Heterogeneous Parallel Networks

### 2025-02-01 thesis/slides.tex
Thesis: Pres: Adds draft slides for all sections
Preliminaries example, Sensitivity split, Pseudo-heterogeneous games, Step distribution functions, Future Work

\begin{frame}{Our model}
	\;
	\begin{block}{$2$-level optimisation problem}
		\begin{enumerate}
			\item Shelfish routing game, flow on minimum cost paths
			\item Profit maximisation game for link owners
		\end{enumerate}
	\end{block}
\end{frame}

@@

\begin{frame}{Heterogeneous players}
	Players value time-money differently, so add weight $\alpha$ to money.
	\begin{block}{Distribution function $\alpha: [0, 1] \rightarrow [0, +\infty]$}
		\begin{itemize}
			\item players are ordered w.r.t. sensitivity
			\item $\alpha$ is non-decreasing
		\end{itemize}
	\end{block}
	Player $p$ experiences on link $i$ total cost $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
	\begin{definition}
		For a given set of tolls $t$, a flow $x$ is a \textit{Nash equilibrium for $t$} if for all players $p \in [0, 1]$ and $\forall i \in N$ it holds that
		\begin{equation*}
			c_{f(p)}(p) \leq c_j(p)
		\end{equation*}
	\end{definition}
\end{frame}

\begin{frame}
	Nash equilibrium for $t$ always exists\footcite{1973JSP.....7..295S} and is unique\footcite{MILCHTAICH1996111}, again denote it by $x(t)$.
\end{frame}

\begin{frame}{Pricing competition (2\textsuperscript{nd} level)}
	Links are owned by agents who compete for profit.
	\begin{block}{Profit}
		For given set of tolls $t \in \R_+^N$, link owner $i$ gains profit
		\[\Pi_i(t) = x_i(t) \cdot t_i\]
	\end{block}

	\begin{block}{Best response}
		For fixed tolls assignments from other link owners $t_{-i} = t \setminus \{t_i\}$, link owner $i$ will try and maximise their profit
		\[B_i(t_{-i}) = \argmax_{t_i \ge 0} \Pi(t_i, t_{-i})\]
	\end{block}
\end{frame}

@@

\begin{frame}{Game equivalence}
	\begin{definition}[Game equivalence]
		Let $\Gm_1, \Gm_2$ be two $n$-link Network Congestion Games.
		$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
	\end{definition}
\end{frame}

@@

\begin{frame}{Sensitivity split}
	\begin{definition}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
		We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
		\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
	\end{definition}
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{block}{Properties}
		περιεχόμενο...
	\end{block}
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{block}{Monotonicity}
		περιεχόμενο...
	\end{block}
\end{frame}

\begin{frame}{Sensitivity split}
	Characterisation.
\end{frame}

@@

\section{Step distribution function}

>>>>

\begin{frame}{Our model}
	\;
	\begin{block}{$2$-level game}
		\begin{enumerate}
			\item Shelfish routing game, flow on minimum cost paths
			\item Profit maximisation game for link operators
		\end{enumerate}
	\end{block}
\end{frame}

@@

\begin{frame}{Heterogeneous players}
	Players value time-money differently, so add weight $\alpha$ to money.
	\begin{block}{Distribution function $\alpha: [0, 1] \rightarrow [0, +\infty]$}
		\begin{itemize}
			\item players are ordered w.r.t. sensitivity
			\item $\alpha$ is non-decreasing
		\end{itemize}
	\end{block}
	Player $p$ experiences on link $i$ total cost $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
	\begin{definition}
		For a given set of tolls $t$, a flow $x$ is a \textit{Nash equilibrium for $t$} if for all players $p \in [0, 1]$ and $\forall i \in N$ it holds that
		\begin{equation*}
			c_{f(p)}(p) \leq c_i(p)
		\end{equation*}
	\end{definition}
\end{frame}

\begin{frame}{Heterogeneous players}
	\begin{example}
		Let $([2], \ell, \alpha)$ with $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and $\alpha(p) = p + 1$.
	\end{example}
	\begin{center}
		\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
			% Nodes
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

			% Links
			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
			\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);

			% Description
			%\node[align=center] at (2, -2) {Network of Example};
		\end{tikzpicture}
	\end{center}
	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
\end{frame}

\begin{frame}{Heterogeneous players}
	Nash equilibrium for $t$ always exists\footcite{1973JSP.....7..295S} and is unique\footcite{MILCHTAICH1996111}, again denote it by $x(t)$.
\end{frame}

\begin{frame}{Pricing competition (2\textsuperscript{nd} level)}
	Links are owned by agents who compete for profit.
	\begin{block}{Profit}
		For given set of tolls $t \in \R_+^N$, link operator $i$ gains profit
		\[\Pi_i(t) = x_i(t) \cdot t_i\]
	\end{block}

	\begin{block}{Best response}
		For fixed tolls assignments from remaining link operators $t_{-i} = t \setminus \{t_i\}$, link operator $i$ will try and maximise their profit
		\[B_i(t_{-i}) = \argmax_{t_i \ge 0} \Pi(t_i, t_{-i})\]
	\end{block}
\end{frame}

@@

\begin{frame}{Game equivalence}
	\begin{definition}[Game equivalence]
		Let $\Gm_1, \Gm_2$ be two $n$-link Network Congestion Games.
		$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
	\end{definition}
	The two pricing competition games played on two equivalent network congestion games are identical.
\end{frame}

@@

\begin{frame}{Sensitivity split}
	In a heterogeneous game, in practice, each flow user plays a different game.

	In example ?? the users are organised around the one for which $c_1(p) = c_2(p)$.

	We need the notion of the money-sensitivity value for which two link costs are equal.
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{definition}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
		We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
		\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
	\end{definition}
	If $t_i = t_j \Leftrightarrow \ell_i(x_i) = \ell_j(x_j)$ then $c_i(p) = c_j(p)$ for \textbf{all} flow users.
\end{frame}

\begin{frame}{Sensitivity split}
	If $t_i \ne t_j$ then assume w.l.o.g. $t_i > t_j \Leftrightarrow \ell_i(x_i) < \ell_j(x_j)$.\\
	Low money-sensitive players will use link $i$.\\
	High money-sensitive players will use link $j$.

	\begin{table}[h!]
		\centering
		\caption{Summary of properties for the sensitivity split.}
		\begin{tabular}{| c || c | c |}
			\hline
			& \textbf{lower split} & \textbf{upper split} \\ \hline
			$\alpha$ & $\alpha(p) \le \as^{(i, j)}(t)$ & $\alpha(p) \ge \as^{(i, j)}(t)$ \\ \hline
			link & low-latency, high-toll & high-latency, low-toll \\ \hline
			sensitivity & time $\ge$ money & time $\le$ money \\ \hline
		\end{tabular}
		\label{table:split_summary}
	\end{table}
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{definition}
		\label{definition:alpha_flow_sets}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ and $x(t)$ the Nash equilibrium for $t$.
		We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
		We define a set function $A_i: \R_+^{|N|} \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
		\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
	\end{definition}

	Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for any $i \in N$.
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{lemma}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
		Then the following hold:
		\begin{enumerate}[(i)]
			\item $\as^{(i, j)}(t) > 0$
			\item $\as^{(i, j)}(t) \in [\alpha(0), \alpha(1)]$
			%\item if $\as^{(i, j)}(t) < \alpha(0)$ (or $\as^{(i, j)}(t) > \alpha(1)$) then $x(t) = (0, 1)$ (or $(1, 0)$)
			\item if $\ell_i(x_i(t)) < \ell_j(x_j(t))$ then
			$\sup A_i(t) \le \as^{(i, j)}(t) \le \inf A_j(t)$
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Sensitivity split | Monotonicity}
	\begin{lemma}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t, t^\prime$ such that for some links $i, j \in N$ it holds that $t_i \ne t_j, t_i^\prime \ne t_j^\prime$ and $t_k = t_k^\prime$ $\forall k \in N \setminus \{i, j\}$.
		If $x_i(t), x_j(t), x_i(t^\prime), x_j(t^\prime) > 0$ and $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0$, then:
		\begin{enumerate}[(i)]
			\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1$ then $\as^{(i, j)}(t) \ge \as^{(i, j)}(t^\prime)$
			\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \ge 1$ then $\as^{(i, j)}(t) \le \as^{(i, j)}(t^\prime)$
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Sensitivity split | Monotonicity}
	\begin{proof}
		We prove $(i)$ and $(ii)$ follows symmetrically.\\
		If $x(t) = x(t^\prime)$ then the property follows from the definition of $\as$.
		If $x(t) \ne x(t^\prime)$ then assume w.l.o.g. that $x_i(t) > x_i(t^\prime)$, so a player $p$ moved from $i$ to $j$ between $t$ and $t^\prime$.
		\[\inf A_j(t^\prime) \le \alpha(p) \le \sup A_i(t)\]
		Applying the previous lemma gives us
		\[\as^{(i, j)}(t^\prime) \le \inf A_j(t^\prime) \le \sup A_i(t) \le \as^{(i, j)}(t)\]
	\end{proof}
\end{frame}

\begin{frame}{Sensitivity split | Limits}
	\begin{lemma}
		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
		Then:
		\begin{enumerate}[(i)]
			\item
			\begin{flalign*}
				\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) &= 0 &
			\end{flalign*}
			\item
			\begin{flalign*}
				\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) &= \limsup_{t_i - t_j \rightarrow 0^+} A_i(t) &
			\end{flalign*}
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Sensitivity split | Limits}
	\begin{proof}
		$ $
		\begin{enumerate}[(i)]
			\item For $L = \max\{\ell_i(1) - \ell_j(0), \ell_j(1) - \ell_i(0)\}$ we find
			\begin{flalign*}
				\lim_{|t_i - t_j| \rightarrow +\infty}|\as^{(i, j)}(t)| &= \lim_{|t_i - t_j| \rightarrow +\infty}\frac{|\ell_i(x_i(t)) - \ell_j(x_j(t))|}{|t_i - t_j|}\\
				&\le \lim_{|t_i - t_j| \rightarrow +\infty}\frac{L}{|t_i - t_j|} = 0
			\end{flalign*}
		\end{enumerate}
	\end{proof}
\end{frame}

\begin{frame}{Sensitivity split | Limits}
	\begin{proof}
		$ $
		\begin{enumerate}[(ii)]
			\item ...
		\end{enumerate}
	\end{proof}
\end{frame}

\begin{frame}{Sensitivity split}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=2cm, y=2cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-1.1,0);
			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,2) -- (-0.05, 2) node[left] {$2$};
			\draw (0,4/3) -- (0.05,4/3) node[right] {$4/3$};
			\draw (0,5/3) -- (-0.05,5/3) node[left] {$5/3$};
			\draw (0,1) -- (-0.05,1) node[left] {$1$};

			% Function graph
			%\draw[thick] (-1,1) -- (0,4/3);
			%\draw[thick] (0,5/3) -- (2,1);
			\draw[thick,domain=-1:0] plot (\x,{4/(3-\x)});
			\draw[thick,domain=0:2] plot (\x,{5/(3+\x)});

			% Dots
			\fill[white] (0,4/3) ellipse (0.03 and 0.03);
			\draw[black] (0,4/3) ellipse (0.03 and 0.03);
			\fill[white] (0,5/3) ellipse (0.03 and 0.03);
			\draw[black] (0,5/3) ellipse (0.03 and 0.03);
		\end{tikzpicture}
		\caption{Split function of Example}
		\label{figure:alpha_simple:split_example}
	\end{figure}
\end{frame}

\begin{frame}{Sensitivity split | Upper bound}
	We observe that $\as$ might never take some upper values of $\alpha$.\\
	Are then those values relevant?

	\begin{theorem}
		Let $\Gm_1 = (N, \ell, \alpha^{(1)})$ and $\Gm_2 = (N, \ell, \alpha^{(2)})$ be two heterogeneous parallel games and $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the (equal) flow on paths for $t = 0$.
		If $\alpha^{(1)}$ and $\alpha^{(2)}$ are such that
		\[\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < 1 - \min_{i \in N}\{x_i(0)\}\]
		then $\Gm_1$ and $\Gm_2$ are equivalent.
	\end{theorem}
\end{frame}

\begin{frame}{Sensitivity split | Upper bound}
	\begin{proof}
		...
	\end{proof}
\end{frame}

\begin{frame}{Sensitivity split | Upper bound}
	For the Example we have
	\[\max\{x_1(0), x_2(0)\} = \max\{2/3, 1/3\} = 2/3\]
	so if we used a distribution function such as
	\[
		\alpha(p) =
		\begin{cases}
			p + 1 & p \le 2/3 \\
			\mathrm{e}^p & p > 2/3
		\end{cases}
	\]
	then $\as(t)$ would remain the same for all $t \in \R_+^n$
\end{frame}

@@

\begin{frame}{Heterogeneous Pricing Games}
	Zero money sensitivity creates issues.
	\begin{lemma}
		Let $(N, \ell, \alpha)$ where $\exists \epsilon > 0: \alpha(p) = 0 \; \forall p < \epsilon$.
		Let $i \in N$ be a link for which $\ell_i(0) = \min_{j \in N} \ell_i(0)$.
		Then $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{|N| - 1}$.
	\end{lemma}
	\begin{proof}
		$\ell_i(0) = \min_{j \in N} \ell_i(0)$, ensures link $i$ will always have flow

		$i$ can select $t_i > \max t_{-i}$ to make link $i$ the lowest-latency link, populated exclusively by players with $\alpha(p) = 0$

		We fix $t_i^\prime$ and we see that
		\[
			\lim_{t_i \rightarrow +\infty} \Pi_i(t_i, t_{-i}) \ge \lim_{t_i \rightarrow +\infty} x_i^\prime(t_i^\prime, t_{-i})t_i = +\infty
		\]
		making in turn $B_i(t_{-i}) = +\infty$.
	\end{proof}
\end{frame}

\begin{frame}{Pseudo-heterogeneous Pricing Games}
	Consider cases where $\alpha(p) = c$ for some $c \in \R_+$.
	\[
		\sum_{i \in N} (\ell(x_i(t)) + c t_i) \cdot (x_i(t) - x_i) \leq 0
	\]

	\begin{lemma}
		Let $\Gm_1 = (N, \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = (N, \ell^{(2)}, 1)$ a homogeneous pricing game with latencies $\ell^{(2)} = \frac{\ell^{(1)}}{c}$ for the same $c$.
		Then the two games are equivalent.
	\end{lemma}
	We will call such games \textit{pseudo-heterogeneous}.

	Latency-sensitivity relation is lost for general $\alpha$
\end{frame}

\begin{frame}{Pseudo-heterogeneous Pricing Games}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-1.1,0);
			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,1.1) node[above] {$x_1(t)$};

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (-1/3,0) -- (-1/3,-0.05) node[left=9,below] {$-\frac13$};
			\draw (-1/4,0) -- (-1/4,-0.05) node[right=3,below] {$-\frac14$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (2/4,0) -- (2/4,-0.05) node[below] {$\frac12$};
			\draw (2/3,0) -- (2/3,-0.05) node[below] {$\frac23$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,1) -- (0.05,1) node[right] {$1$};
			\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};

			% Flow function graphs
			\draw[thick, blue!33] (-1,1) -- (2,0) node[above, black] {$\alpha = 1$};
			\draw[thick, blue!66] (-1/3,1) -- (2/3,0) node[above right, black] {$\alpha = 3$};
			\draw[thick, blue!100] (-1/4,1) -- (2/4,0) node[black] at (0.2,0.17) {$\alpha = 4$};
		\end{tikzpicture}
		\caption{Flow function for link $1$ of Example for $\alpha(p) = 1, 3, 4$.}
	\end{figure}
\end{frame}

\begin{frame}{Pseudo-heterogeneous Pricing Games}
	\begin{lemma}
		Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with $\alpha^{(1)}(p) = c_1 > 0$, $\alpha^{(2)}(p) = c_2 > 0$, then
		\begin{enumerate}[$(i)$]
			%\item $x^{(1)}(0) = x^{(2)}(0)$
			\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
			\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
			\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Pseudo-heterogeneous Pricing Games}
	\begin{lemma}
		Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with $\alpha^{(1)}(p) = c_1 > 0$, $\alpha^{(2)}(p) = c_2 > 0$.\\
		Let $t^{*(1)}, t^{*(2)}$ the Nash Equilibria for the pricing games in $\Gm_1$ and $\Gm_2$.
		Then
		\begin{enumerate}[$(i)$]
			\item $\frac{t^{*(1)}}{t^{*(2)}} = \frac{c_2}{c_1}$
			\item $x^{(1)}(t^{*(1)}) = x^{(2)}(t^{*(2)})$
		\end{enumerate}
	\end{lemma}
	Nash Equilibrium always at the same flow.
\end{frame}

\section{Step distribution functions}

\begin{frame}{Step distribution functions}
	We will limit our model to instances with $2$ links.

	In $2$-link games, $\as(t)^{(1, 2)} = \as(t)$.

	There always exists an $\alpha$ value for which the two link costs are equal.
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{lemma}
		Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls and $x^{(1)}(t)$ the Nash equilibrium for $t$.
		Now let $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a pseudo-heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
		Then
		\begin{enumerate}[$(i)$]
			\item $x^{(1)}(t) = x^{(2)}(t)$
			\item $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$ for each respective link operator $i$
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{example}
		Let $([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
		\begin{align*}
			\alpha(p) =
			\begin{cases}
				1 & p \le \tfrac15 \\
				3 & p \in \left(\tfrac15, \tfrac12\right) \\
				4 & p \ge \tfrac12
			\end{cases}&
		\end{align*}
	\end{example}

	\begin{center}
		\begin{multicols}{2}
			% Left Column: Network Graph
			\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
				% Nodes
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};

				% Links
				\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
				\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);

				% Description
				\node[align=center] at (2, -2) {Network of Example};
			\end{tikzpicture}

			% Right Column: Distribution function Graph
			\begin{tikzpicture}[x=3cm, y=0.7cm, every node/.style={font=\small}]
				% Axes
				\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
				\draw[->] (0,0) -- (0,4.2) node[above] {$\as(p)$};

				% Tick marks
				\draw (0,0) -- (0,-0.05) node[below] {$0$};
				\draw (0.2,0) -- (0.2,-0.05) node[below] {$\frac15$};
				\draw (0.5,0) -- (0.5,-0.05) node[below] {$\frac12$};
				\draw (1,0) -- (1,-0.05) node[below] {$1$};
				\draw (0,1) -- (-0.05,1) node[left] {$1$};
				\draw (0,3) -- (-0.05,3) node[left] {$3$};
				\draw (0,4) -- (-0.05,4) node[left] {$4$};

				% Function graph
				\draw[thick] (0,1) -- (0.2,1);
				\draw[thick] (0.2,3) -- (0.5,3);
				\draw[thick] (0.5,4) -- (1,4);

				% Closed / Open dots
				\fill[white] (0.2,1) ellipse (0.014 and 0.06);
				\draw[black] (0.2,1) ellipse (0.014 and 0.06);
				\fill[black] (0.2,3) ellipse (0.014 and 0.06);
				\draw[black] (0.2,3) ellipse (0.014 and 0.06);
				\fill[black] (0.5,3) ellipse (0.014 and 0.06);
				\draw[black] (0.5,3) ellipse (0.014 and 0.06);
				\fill[white] (0.5,4) ellipse (0.014 and 0.06);
				\draw[black] (0.5,4) ellipse (0.014 and 0.06);

				% Description
				\node[align=center] at (0.7, -1.7) {Distribution function of Example};
			\end{tikzpicture}
		\end{multicols}
	\end{center}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=3.4cm, y=1cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-1.1,0);
			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,4.4) node[above] {$\as(t)$};

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,1) -- (-0.05,1) node[left] {$1$};
			\draw (0,3) -- (0.05,3) node[right] {$3$};
			\draw (0,4) -- (-0.05,4) node[left] {$4$};

			% Function graph
			% Left side
			\draw[thick] (-1,1) -- (-2/5,1);
			\draw[thick] (-2/5,1) -- (-2/15,3);
			\draw[thick] (-2/15,3) -- (0,3);
			% Right side
			\draw[thick] (0,4) -- (1/8,4);
			\draw[thick] (1/8,4) -- (1/6,3);
			\draw[thick] (1/6,3) -- (7/15,3);
			\draw[thick] (7/15,3) -- (7/5,1);
			\draw[thick] (7/5,1) -- (2,1);

			% Dots
			\fill[white] (0,3) ellipse (0.02 and 0.066);
			\draw[black] (0,3) ellipse (0.02 and 0.066);
			\fill[white] (0,4) ellipse (0.02 and 0.066);
			\draw[black] (0,4) ellipse (0.02 and 0.066);
		\end{tikzpicture}
		\caption{Split function of Example}
		\label{figure:alpha_step:split}
	\end{figure}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-1.1,0);
			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,1.1) node[above] {$x_1(t)$};

			% Tick marks
			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
			\draw (2,0) -- (2,-0.05) node[below] {$2$};
			\draw (0,1) -- (-0.05,1) node[left] {$1$};
			\draw (0,4/5) -- (0.05,4/5) node[right] {$\frac45$};
			\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};
			\draw (0,1/2) -- (-0.05,1/2) node[left] {$\frac12$};
			\draw (0,1/5) -- (-0.05,1/5) node[left] {$\frac15$};

			% Function graph
			% Base flow functions
			\draw[gray,dashed, very thin] (-1,1) -- (2,0);
			\draw[gray,dashed, very thin] (-1/3,1) -- (2/3,0);
			\draw[gray,dashed, very thin] (-1/4,1) -- (2/4,0);

			% Left side
			\draw[thick] (-1,1) -- (-2/5,4/5);
			\draw[thick] (-2/5,4/5) -- (-2/15,4/5);
			\draw[thick] (-2/15,4/5) -- (0,2/3);
			% Right side
			\draw[thick] (0,2/3) -- (1/8,1/2);
			\draw[thick] (1/8,1/2) -- (1/6,1/2);
			\draw[thick] (1/6,1/2) -- (7/15,1/5);
			\draw[thick] (7/15,1/5) -- (7/5,1/5);
			\draw[thick] (7/5,1/5) -- (2,0);
		\end{tikzpicture}
		\caption{Flow function for link $1$ of Example}
		\label{figure:alpha_step:flow}
	\end{figure}
\end{frame}

\begin{frame}{Step distribution functions}
	Notice that when $x_1$ is fixed then $\as$ isn't and vice-versa.\\
	If the flow is moving, then it does so among players with the same sensitivity type, which is one of the finitely many values $\alpha$ can take.
	If all players of each sensitivity type are using a single link, then $\as$ can take any value between the lowest and highest $\alpha$ value in the upper and lower split respectively.
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{theorem}
		Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous pricing game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
		If $\Gm_1$ has a Nash equilibrium for the pricing game at toll $t^*$, let $\Gm_2 = ([2], \ell, \as(t^*))$ a pseudo-heterogeneous game with latency functions the same as the ones in $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as(t^*)$.
		Then $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
	\end{theorem}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{example}
		Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
		\begin{align*}
			\alpha(p) =
			\begin{cases}
				3 & p \le \tfrac14 \\
				4 & p > \tfrac14
			\end{cases}&
		\end{align*}
		Then $\Gm$ has a Nash Equilibrium for the pricing game at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
	\end{example}
\end{frame}

\begin{frame}{Step distribution functions}
	\begin{figure}
		\centering
		\begin{tikzpicture}[x=8cm, y=10cm, every node/.style={font=\small}]
			% Axes
			\draw[->] (0,0) -- (-0.4,0);
			\draw[->] (0,0) -- (0.7,0) node[right] {$t_1 - t_2$};
			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1(t)$};

			% Tick marks
			\draw (-1/3,0) -- (-1/3,-0.01) node[below] {$-\frac13$};
			\draw (-1/4,0) -- (-1/4,-0.01) node[below] {$-\frac14$};
			\draw (-1/12,0) -- (-1/12,-0.01) node[left=9,below] {$-\frac{1}{12}$};
			\draw (-1/16,0) -- (-1/16,-0.01) node[right=2,below] {$-\frac{1}{16}$};
			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_2^* = \frac{4}{12}$};
			\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
			\draw (5/16,0) -- (5/16,-0.01) node[below] {$\frac{5}{16}$};
			\draw (5/12,0) -- (5/12,-0.01) node[below] {$\frac{5}{12}$};
			\draw (2/4,0) -- (2/4,-0.01) node[below] {$\frac24$};
			\draw (2/3,0) -- (2/3,-0.01) node[below] {$\frac23$};
			%\draw (0,2/9) -- (-0.02,2/9) node[left] {$\frac29$};
			%\draw (0,1/12) -- (0.01,1/12) node[right] {$\frac{1}{12}$};

			% Pseudo-heterogeneous profits
			\draw[gray,dashed,thick,domain=-1/3:2/3] plot (\x,{((2-3*\x)/3)*(1/3+\x)}) node[above=17,right=-7,black] {$c = 3$};
			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=10,right=-3,black] {$c = 4$};
